Radio Emission from Red-Giant Hot Jupiters

### 2015-12-27 ms.tex
affiliation revised

\def\revise#1{\color{blue}{\bf #2} \color{black}}

@@

\author{
%
Yuka Fujii\altaffilmark{1} 
%
David S. Spiegel\altaffilmark{2,3,4}
%
Tony Mroczkowski\altaffilmark{5,6}
%
Jason Nordhaus\altaffilmark{7,8}\\
%
Neil T. Zimmerman\altaffilmark{9}
%
Aaron Parsons\altaffilmark{10}
%
Mehrdad Mirbabayi\altaffilmark{4}
%
Nikku Madhusudhan\altaffilmark{11}
}

@@

\affil{$^2$Analytics \& Algorithms, Stitch Fix,
  San Francisco, CA  94103}

\affil{$^3$Research \& Development, Sum Labs,
  New York, NY  10001}

\affil{$^4$Astrophysics Department, Institute for Advanced Study,
  Princeton, NJ 08540}

\affil{$^5$National Research Council Fellow}

\affil{$^6$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}

\affil{$^7$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^8$Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^9$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}

\affil{$^{10}$Astronomy Department, University of California Berkeley}

\affil{$^{11}$Astronomy Department, University of Cambridge, UK}
\vspace{0.5\baselineskip}

>>>>

\def\revise#1{\color{blue}{\bf #1} \color{black}}

@@

\author{
%
Yuka Fujii\altaffilmark{1,2} 
%
David S. Spiegel\altaffilmark{3,4,5}
%
Tony Mroczkowski\altaffilmark{6,7}
%
Jason Nordhaus\altaffilmark{8,9}\\
%
Neil T. Zimmerman\altaffilmark{10}
%
Aaron Parsons\altaffilmark{11}
%
Mehrdad Mirbabayi\altaffilmark{5}
%
Nikku Madhusudhan\altaffilmark{12}
}

@@

\affil{$^2$NASA Goddard Institute for Space Studies, 
  New York, NY 10025}

\affil{$^3$Analytics \& Algorithms, Stitch Fix,
  San Francisco, CA  94103}

\affil{$^4$Research \& Development, Sum Labs,
  New York, NY 10001}

\affil{$^5$Astrophysics Department, Institute for Advanced Study,
  Princeton, NJ 08540}

\affil{$^6$National Research Council Fellow}

\affil{$^7$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}

\affil{$^8$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^9$Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^10$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}

\affil{$^{11}$Astronomy Department, University of California Berkeley}

\affil{$^{12}$Astronomy Department, University of Cambridge, UK}
\vspace{0.5\baselineskip}
